---
title: "RWorksheet_Cacho_Perez_Sorenio_Tupaz"
output: pdf_document
date: "2024-11-11"
---

Extracting TV Shows Reviews

1. Each group needs to extract the top 50 tv shows in Imdb.com. It will include the rank, the title of the tv show, tv rating, the number of people who voted, the number of episodes, the year it was released. It will also include the number of user reviews and the number of critic reviews, as well as the popularity rating for each tv shows.

2. From the 50 tv shows, select at least 5 tv shows to scrape 20 user reviews that will include the reviewer’s name, date of reviewed, user rating, title of the review, the numbers for “is helpful” and “is not helpful”, and text reviews.

3. Create a time series graph for the tv shows released by year. Which year has the most number of tv shows released?

```{r}
# install.packages("rvest")
# install.packages("httr")
# install.packages("polite")

library(rvest)
library(httr)
library(dplyr)

library(polite)

#install.packages("kableExtra")
#library(kableExtra)
#library(rmarkdown)
```

```{r}
polite::use_manners(save_as = 'polite_scrape.R')
```

```{r}
url <- 'https://www.imdb.com/chart/toptv/?ref_=nv_tvv_250&sort=rank%2Casc'
session <- bow(url,
               user_agent = "Educational")
session
```

```{r}
rank_title <- character(0)
links <- character(0)
```

```{r}
title_list <- scrape(session) %>%
  html_nodes('h3.ipc-title__text') %>% 
  html_text()
```

```{r}
class(title_list)
```

```{r}
title_listSub <- as.data.frame(title_list[2:26])
head(title_listSub)
tail(title_listSub)
```

```{r}
colnames(title_listSub) <- "ranks"

split_title <- strsplit(as.character(title_listSub$ranks),".",fixed = TRUE)
split_title <- data.frame(do.call(rbind,split_title))
```

```{r}
split_title <- split_title[-c(3:4)]
```

```{r}
colnames(split_title) <- c("Rank","Title") 
```

```{r}
str(split_title) 
head(split_title)
```

```{r}
rank_title <- data.frame(rank_title = split_title)
```

```{r}
write.csv(rank_title,file = "D:/Files/title.csv")
```

```{r}
linkList <- scrape(session) %>%
  html_nodes('a.ipc-title-link-wrapper') %>% 
  html_attr('href') 
```

```{r}
linkList <- linkList[!is.na(linkList) & linkList != ""]
```

```{r}
for (i in 1:length(linkList)) {
  linkList[i] <- paste0("https://imdb.com", linkList[i])
}
```

```{r}
links <- as.data.frame(linkList)
names(links) <- "link"

rank_title <- data.frame(rank_title = split_title)
```

```{r}
scrape_rankTitle <- data.frame(rank_title)
names(scrape_rankTitle) <- c("Rank", "Title")

head(scrape_rankTitle)
write.csv(scrape_rankTitle,file = "D:/Files/top250.csv")
```

```{r}
current_row <- 1
imdbTop25 <- data.frame()

for (row in 1:25) {
  url <- links$link[current_row]
}

  if (url == "" || is.na(url)) {
    next
  }
```

```{r}
 session2 <- bow(url, user_agent = "Educational")
  webpage <- scrape(session2)
```

```{r}
ratings <- html_text(html_nodes(webpage, ".sc-d541859f-1.imUuxf"))
  if (length(ratings) == 0) {
    next
  } else {
    ratings <- ratings[1]
  }
```

```{r}
votes <- html_text(html_nodes(webpage, 'div.sc-d541859f-3.dwhNqC'))
  if (length(votes) == 0) {
    next
  } else {
    votes <- votes[1]
  }
```

```{r}
episodesperYear <- html_text(html_nodes(webpage, xpath = "//span[contains(text(), 'episodes')]"))
  if (length(episodesperYear) == 0) {
    next
  } else {
    episodesperYear <- episodesperYear[1]
    episodes <- sub("episodes.*", "episodes", episodesperYear)
    yearReleased <- sub(".*episodes • ", "", episodesperYear)
  }
```

```{r}
cat("Rating for", url, "is:", ratings, "vote count is", votes, "number of episodes is", episodes, "year released is", yearReleased, "\n")
```

```{r}
imdbTop25[current_row, 1] <- ratings
  imdbTop25[current_row, 2] <- votes
  imdbTop25[current_row, 3] <- episodes
  imdbTop25[current_row, 4] <- yearReleased
```

```{r}
current_row <- current_row + 1
```

```{r}
names(imdbTop25) <- c("Rating","Votes","Number of Episodes", "Year Released")
```

```{r}
write.csv(imdbTop25,file = "D:/Files/imdbTop25.csv")
```

```{r}
imdbTop25 <- data.frame(scrape_rankTitle, imdbTop25)

write.csv(imdbTop25,file = "D:/Files/imdbTop250.csv")
library(kableExtra)
```

```{r}
knitr::kable(imdbTop25,caption = "Extracting Rating, Votes, Number of Episodes, Year Released") %>%
  kable_classic(full_width = FALSE, html_font = "Times New Roman") %>%
  kable_styling(font_size = 13)
library(kableExtra)
```

```{r}
top25 <- imdbTop25[c(1:25),]

top25 <- top25 %>%
  select_if(~ !all(is.na(.)))

knitr::kable(top25, caption = "IMDB Top 25 Shows") %>%
  kable_classic(full_width = FALSE, html_font = "Times New Roman") %>%
  kable_styling(font_size = 13)
```

